\documentclass{article}
\usepackage{graphicx}
\title{HELLO Cruel world.}
\begin{document}
 \section{chapter1}
 
 chapter1
@ This is the section that is invariably much longer than it should be and
where everyone tries to impress peers about how easy it is to locate various references in online database

\subsection{Chapter 2.1 Monetization}

Monetization also written monetisation is the process of converting or establishing something into legal tender. While it usually refers to the coining of currency or the printing of banknotes by central banks it may also take the form of a promissory currency. \par

\begin{enumerate}
 \item car
 	\begin{enumerate}
  	\item anshu
 	 \item garima
	  \item sarthak
 	\end{enumerate}

	\begin{enumerate}
  	\item anshu
 	 \item garima
	  \item sarthak
 	\end{enumerate}

 \item train
  \item bus
  \item bike
\end{enumerate}


The term monetization figure may also be used informally to refer to exchanging possessions for cash or cash equivalent including selling a security interest charging fees for something that used to be free or attempting to make money on goods or services that were previously unprofitable or had been considered to have the potential to earn profits. And data monetization refers to a spectrum of ways information assets can be converted into economic value. 

\begin{table}
	\caption{Table with raw data}
	\label{tab1}
    \begin{tabular}{l|c|r}
      \textbf{Value 1} & \textbf{Value 2} & \textbf{Value 3} \\
      1 & 46.9 & g\\
      2 & 10.8 & b\\
      3 & 23.5 & c\\
      4 & 7.20 & a\\
\end{tabular}
 \end{table}


 [] Still another meaning of monetization denotes the process by which the U.S. Treasury accounts for the() * + - / \%  face value of outstanding coina ge. This procedure can extend even to oneofakind situations such as when the Treasury Department sold an extremely rare 1933 Double Eagle.\\ The coin nominal value I dont know.

\subsection{Chapter 2.2 Artificial Intelligence}

Artificial intelligence sometimes called machine intelligence is intelligence demonstrated by machines in contrast to the natural intelligence displayed by humans and @ other animals. In computer science AI research is defined as the study of intelligent agents any device that perceives its environment and takes actions that maximize its chance of successfully\{ achieving its [ goals.

$ \sqrt{\frac{67}{ai}} $
$ \sqrt{45}$
$ \sum_i \frac{a_i}{1x}  $

$ f(x) = \sum_{i}^{n} \frac{a_i}{1x} $
$ \int_{1}^{2} hh dx $
$ \alpha \beta \pi \Pi \gamma \delta $ 

Some of the \textbf{greatest}      
discoveries in     \underline{science}                 
were made by          \textbf{\textit{accident}}.

$ \frac{ai}{1x} $
$ \sqrt56$
$ \frac{\sqrt{46}}{89}$

\section{Chapter 3 Conclusion.}

Not much of a  paper but its a start.


\begin{table}
	\caption{Table with raw data}
	\label{tab2}
    \begin{tabular}{l|c|r}
      \textbf{Value 1} & \textbf{Value 2} & \textbf{Value 3} \\
      1 & 46.9 & g\\
      2 & 10.8 & b\\
      3 & 23.5 & c\\
      4 & 7.20 & a\\
\end{tabular}
 \end{table}

plz rerfer table \ref{tab2} and \ref{tab1}.
 
\end{document}
